A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
Remove server table
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1012 43ef1190-90fd-4dd7-a769-d0121f02b80e

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness time or a promising feature. For
the former, this amounted to 22 servers, see 
Table~\ref{tab:servers}. 70 servers always responded with promising
features. As we can see, apart from well-known Virtuoso and
Callimachus servers, as well as the Perl modules RDF::LinkedData and
RDF::Endpoint, which is partly developed by and runs on a server
operated by this author, most headers tell very little about the
RDF-specific parts of the underlying server implementation. A quick
inspection of all \httph{Server} headers confirmed that few reveal any
further detail.

% latex table generated in R 2.15.1 by xtable 1.5-6 package
% Mon Jan  5 11:27:35 2015
\begin{table}[h]
  \caption{\httph{Server} headers for hosts that enabled a freshness
    lifetime to be computed for \emph{all} requests.}\label{tab:servers}
\begin{center}
\begin{tabular}{rl}
  \hline
1 & DFE/largefile \\ 
  2 & git\_frontend \\ 
  3 & nginx/1.3.9 \\ 
  4 & thin 1.6.0 codename Greek Yogurt \\ 
  5 & Oracle-Application-Server-10g/10.1.3.4.0 Oracle-HTTP-Server [\ldots]\\
  6 & Oracle-Application-Server-10g/10.1.3.4.0 Oracle-HTTP-Server [\ldots]\\
  7 & TwistedWeb/8.2.0 \\ 
  8 & RDF::Endpoint/0.07 \\ 
  9 & Jetty(6.1.26) \\ 
  10 & nginx/1.6.1 \\ 
  11 & Jigsaw/2.3.0-beta3 \\ 
  12 & Apache/2.2.9 (Win32) PHP/5.2.6 \\ 
  13 & Apache/2.4.10 (Unix) mod\_fcgid/2.3.9 \\ 
  14 &  \\ 
  15 & GFE/2.0 \\ 
  16 & RDF::LinkedData/0.70 \\ 
  17 & Apache/2.2.17 (Unix) mod\_wsgi/3.3 Python/2.6.6 \\ 
  18 & Virtuoso/07.10.3211 (Linux) i686-generic-linux-glibc212-64  VDB \\ 
  19 & Apache/2.2.24 (Unix) mod\_ssl/2.2.24 OpenSSL/0.9.8y \\ 
  20 & Apache/2.2.22 (Fedora) \\ 
  21 & INSEE \\ 
  22 & GitHub.com \\ 
   \hline
\end{tabular}
\end{center}
\end{table}

>>>>

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness time or a promising\todo{what are
  they} feature. For the former, this amounted to 22 servers. 70
servers always responded with promising features. Inspecting the
values we find the well-known Virtuoso and Callimachus servers, as
well as the Perl modules RDF::LinkedData and RDF::Endpoint, which is
partly developed by and runs on a server operated by this
author. Apart from those, a typical server string is
e.g. \httph{Apache/2.2.22 (Fedora)}, which reveals very little about
the RDF-specific parts of the underlying server implementation. A
quick inspection of all \httph{Server} headers confirmed that few
reveal any further detail.
